### 2020-04-10 system-model.tex
:pencil: Fix composite channel model

		Denote the baseband equivalent channels from the AP to users, from the AP to the IRS, and from the IRS to users as $\boldsymbol{H}_D \in \mathbb{C}^{K \times N}$, $\boldsymbol{H}_I \in \mathbb{C}^{L \times N}$, and $\boldsymbol{H}_R \in \mathbb{C}^{K \times NL}$ respectively. At subband $n$, the frequency response of direct and reflective links are $\boldsymbol{h}_{D,n}=[h_{D,n,1},\dots,h_{D,n,K}]^T \in \mathbb{C}^{K \times 1}$ and $\boldsymbol{h}_{R,n}=[\boldsymbol{h}_{R,n,1},\dots,\boldsymbol{h}_{R,n,L}] \in \mathbb{C}^{K \times L}$, with $\boldsymbol{h}_{R,n,l}=[h_{R,n,l,1},\dots,h_{R,n,l,k}]^T \in \mathbb{C}^{K \times 1}$. 'Similarly, the $n$-th incident channel matrix writes as $\boldsymbol{h}_{I,n}=[h_{I,n,1},\dots,h_{I,n,L}]^T \in \mathbb{C}^{L \times 1}$. Element $l$ of the IRS receives a superposed waveform through the multipath channel and redistributes it by adjusting the amplitude reflection coefficient $\beta_l \in [0,1]$ and phase shift $\theta_l \in [0,2\pi)$. Each passive reflector absorbs a small portion ($1 - \beta_l$) of the signal to support CSI decoding and impedance matching. Construct a diagonal subband-wise IRS matrix by collecting all reflection coefficients onto the diagonal entries such that $\boldsymbol{\Theta}_0 = \text{diag}(\beta_1 e^{j \theta_1}, \dots, \beta_L e^{j \theta_L}) \in \mathbb{C}^{L \times L}$. With the assumption of frequency-flat reflection, the IRS matrix is formed by stacking $\boldsymbol{\Theta}_0$ over $N$ subbands such that $\boldsymbol{\Theta} = [\boldsymbol{\Theta}_0^T,\dots,\boldsymbol{\Theta}_0^T]^T \in \mathbb{C}^{NL \times L}$. The IRS-aided extra link can be modeled as a concatenation of the AP-IRS channel, the IRS reflection matrix, and the IRS-user channel. Both direct and AP-IRS-user link contributes to the composite channel $\boldsymbol{H} \in \mathbb{C}^{K \times N}$ as
		\begin{equation}	\label{eq:H}
			\boldsymbol{H} = \boldsymbol{H}_D+\boldsymbol{H}_R\boldsymbol{\Theta}\boldsymbol{H}_I
		\end{equation}
		Hence, the $n$-th subchannel $\boldsymbol{h}_n \in \mathbb{C}^{K \times 1}$ is
		\begin{equation}	\label{eq:h_n}
			\boldsymbol{h}_n=\boldsymbol{h}_D+\boldsymbol{H}_{R}\boldsymbol{\Theta}_0\boldsymbol{h}_{I,n}
		\end{equation}
		It is interesting to notice that the reflective channel across all $N$ subbands influences the overall frequency response at subband $n$.
	\end{subsection}

	\begin{subsection}	{Received Signal}
		The RF signal received by user $k$ captures the contribution of information and power waveforms through both direct and reflective links as
		\begin{equation}	\label{eq:y_{k}(t)}
			\begin{split}
				y_{k}(t)
				&=\sum_{m=1}^M{y_{k,m}(t)}	\\
				&=\Re\left\{\sum_{m=1}^M{\sum_{n=1}^N{(w_{I,n,m}\tilde{x}_{I,n}(t)+w_{P,n,m})h_{k,n,m}e^{j2{\pi}{f_n}t}}}\right\}	\\
				&=\Re\left\{\sum_{n=1}^N{\boldsymbol{h}_{k,n}(\boldsymbol{w}_{P,n}+\boldsymbol{w}_{I,n}\tilde{x}_n)e^{j2{\pi}{f_n}t}}\right\}	\\
				&=y_{I,k}(t)+y_{P,k}(t)
			\end{split}
		\end{equation}
	\end{subsection}

	\begin{subsection}	{Information Decoder}
		One major benefit of using proposed waveform is that the deterministic power term $y_{P,k}(t)$ bears no information and creates no interference to the modulated information term $y_{I,k}(t)$. Therefore, the achievable rate of user $k$ is expressed as
		\begin{equation}	\label{eq:I_k}
			\begin{split}
				I_k(\boldsymbol{w}_I,\boldsymbol{\Theta},\rho)
				&=\sum_{n=1}^N{\log_2\left(1+\frac{(1-\rho)\lvert\boldsymbol{h}_{k,n}\boldsymbol{w}_{I,n}\rvert^2}{\sigma_n^2}\right)}	\\
				&=?
			\end{split}
		\end{equation}
		where $\sigma_n^2$ is the sum variance of the Gaussian noise at the RF-band and those introduced during the RF-to-BB conversion on subband $n$. A significant conclusion in \cite{Clerckx2018b} indicates that the rate \ref{eq:I_k} is always achievable with or without waveform cancellation, by subtracting the deterministic power component or constructing a translated codebook.
	\end{subsection}

	\begin{subsection}	{Energy Harvester}
		Although the power term $y_{P,k}(t)$ have no impact on communication, both $y_{I,k}(t)$ and $y_{P,k}(t)$ contribute to energy delivery in different manner. Consider the nonlinear diode model based on the Taylor expansion of a small signal model \cite{Clerckx2018b,Clerckx2016a}, which highlights the dependency between the harvester output DC current and the received waveform by
		\begin{equation}	\label{eq:i_k}
			i_{\text{out},k}\approx\sum_{i=0}^{\infty}{k_i'}{R_{\text{ant}}^{i/2}}{\mathcal{E}\left\{y_k(t)^i\right\}}
		\end{equation}
		where $k_i'$ depends on $i_{\text{out},k}$ and diode characteristics, $R_{\text{ant}}$ is the impedance of receive antenna. With the assumption of evenly spaced frequencies, $\mathcal{E}\left\{y(t)^i\right\}=0$ for odd $i$ which has no contribution to DC components. \cite{Clerckx2016a} also demonstrated that to maximize $i_{\text{out},k}$, it suffices to maximize the monotonic target function truncated to the $n_0$ order
		\begin{equation}	\label{eq:z_{DC,k}}
			\begin{split}
				z_{DC,k}
				&=\sum_{i\,\text{even},i\ge2}^{n_0}{k_i}{R_{\text{ant}}^{i/2}}{\mathcal{E}\left\{y_k(t)^i\right\}}	\\
				&=\sum_{i\,\text{even},i\ge2}^{n_0}{k_i}{R_{\text{ant}}^{i/2}}{\mathcal{E}\left\{y_{P,k}(t)^i\right\}}	\\
				&+\sum_{i\,\text{even},i\ge2}^{n_0}{k_i}{R_{\text{ant}}^{i/2}}{\mathcal{E}\left\{\mathcal{A}\left\{y_{I,k}(t)^i\right\}\right\}}
			\end{split}
		\end{equation}
		where $k_i=i_s/i!(nv_t)^i$, $i_s$ is saturation current, $n$ is diode ideality factor, $v_t$ is thermal voltage.

>>>>

		Denote the baseband equivalent channels from the AP to users, from the AP to the IRS, and from the IRS to users as $\boldsymbol{H}_D \in \mathbb{C}^{K \times N}$, $\boldsymbol{H}_I' \in \mathbb{C}^{L \times N}$, and $\boldsymbol{H}_R \in \mathbb{C}^{K \times NL}$ respectively. At subband $n$, the frequency response of direct and reflective links write as $\boldsymbol{h}_{D,n}=[h_{D,1,n},\dots,h_{D,K,n}]^T \in \mathbb{C}^{K \times 1}$ and $\boldsymbol{H}_{R,n}=[\boldsymbol{h}_{R,1,n}^T,\dots,\boldsymbol{h}_{R,K,n}^T]^T \in \mathbb{C}^{K \times L}$ with $\boldsymbol{h}_{R,k,n}=[h_{R,k,n,1},\dots,h_{R,k,n,L}] \in \mathbb{C}^{1 \times L}$. Similarly, the $n$-th incident channel is given by $\boldsymbol{h}_{I,n}=[h_{I,n,1},\dots,h_{I,n,L}]^T \in \mathbb{C}^{L \times 1}$. To decouple the impact of IRS operation on the incident link, we construct a block-diagonal matrix $\boldsymbol{H}_I \triangleq \text{diag}\left\{\boldsymbol{h}_{I,1},\dots,\boldsymbol{h}_{I,N}\right\} \in \mathbb{C}^{NL \times N}$. Element $l$ of the IRS receives a superposed waveform through the multipath channel, then redistributes it by adjusting the amplitude reflection coefficient $\beta_l \in [0,1]$ and phase shift $\theta_l \in [0,2\pi)$. Each passive reflector absorbs a small portion ($1 - \beta_l$) of the signal to support CSI decoding and impedance matching. On top of this, the IRS matrix of each subband is constructed by collecting the reflection coefficients onto its diagonal entries as $\boldsymbol{\Theta}_0 = \text{diag}\left\{\beta_1 e^{j \theta_1}, \dots, \beta_L e^{j \theta_L}\right\} \in \mathbb{C}^{L \times L}$. Finally, the IRS matrix is formed by $\boldsymbol{\Theta} = \text{diag}\{\underbrace{\boldsymbol{\Theta}_0,\dots,\boldsymbol{\Theta}_0}_{N\text{ times}}\} \in \mathbb{C}^{NL \times NL}$. The IRS-aided extra link can be modeled as a concatenation of the AP-IRS channel, the IRS reflection matrix, and the IRS-user channel. Both direct and IRS-aided link contributes to the composite channel $\boldsymbol{H} \in \mathbb{C}^{K \times N}$ as

		% We also denote the direct and reflective links of user $k$ as $\boldsymbol{h}_{D,k}=[h_{D,k,1},\dots,h_{D,k,N}] \in \mathbb{C}^{1 \times N}$ and $\boldsymbol{h}_{R,k}=[\boldsymbol{h}_{R,k,1},\dots,\boldsymbol{h}_{R,k,N}] \in \mathbb{C}^{1 \times NL}$ with $\boldsymbol{h}_{R,k,n}=[h_{R,k,n,1},\dots,h_{R,k,n,L}] \in \mathbb{C}^{1 \times L}$. Therefore, it holds that $\boldsymbol{H}_D=[\boldsymbol{h}_{D,1},\dots,\boldsymbol{h}_{D,N}]=[\boldsymbol{h}_{D,1}^T,\dots,\boldsymbol{h}_{D,K}^T]^T$, $\boldsymbol{H}_I=[\boldsymbol{h}_{I,1},\dots,\boldsymbol{h}_{I,N}]$, and $\boldsymbol{H}_R=[\boldsymbol{H}_{R,1},\dots,\boldsymbol{H}_{R,N}]=[\boldsymbol{h}_{R,1}^T,\dots,\boldsymbol{h}_{R,K}^T]^T$.

		% [\boldsymbol{h}_{R,n,1},\dots,\boldsymbol{h}_{R,n,L}] \in \mathbb{C}^{K \times L}$ with $\boldsymbol{h}_{R,n,l}=[h_{R,1,n,l},\dots,h_{R,K,n,l}]^T \in \mathbb{C}^{K \times 1}$.
		% , which is further divided into horizontal submatrices $\boldsymbol{\Theta}_n \in \mathbb{C}^{NL \times L}$ such that $\boldsymbol{\Theta}=[\boldsymbol{\Theta}_1,\dots,\boldsymbol{\Theta}_N]$.
		% , which is then divided into $N$ vertical submatrices $\boldsymbol{H}_{I,n} \in \mathbb{C}^{L \times N}$ such that $\boldsymbol{H}_{I}=[\boldsymbol{H}_{I,1}^T,\dots,\boldsymbol{H}_{I,N}^T]^T$.
		% whose $n$-th column denotes the zero-padded incident subchannel $\boldsymbol{h}_{I,n}=[\boldsymbol{0}_{1 \times (n-1)L}^T, \boldsymbol{h}_{I,n}'^T,\boldsymbol{0}_{1 \times (N-n)L}^T]^T \in \mathbb{C}^{NL \times 1}$.

		\begin{equation}	\label{eq:H}
			\boldsymbol{H} = \boldsymbol{H}_D+\boldsymbol{H}_R\boldsymbol{\Theta}\boldsymbol{H}_I
		\end{equation}
		whose $(k,n)$-th entry
		\begin{equation}	\label{eq:h_{k,n}}
			h_{k,n}=h_{D,k,n}+\boldsymbol{h}_{R,k,n}\boldsymbol{\Theta}_0\boldsymbol{h}_{I,n}
		\end{equation}
		represents the overall channel gain of user $k$ at subband $n$. On top of this, the $n$-th subchannel for all users $\boldsymbol{h}_n \in \mathbb{C}^{K \times 1}$ can be expressed as
		\begin{equation}	\label{eq:h_n}
			\boldsymbol{h}_n=\boldsymbol{h}_{D,n}+\boldsymbol{H}_{R,n}\boldsymbol{\Theta}_0\boldsymbol{h}_{I,n}
		\end{equation}
	\end{subsection}

	\begin{subsection}	{Received Signal}
		The RF signal received by user $k$ captures the contribution of information and power waveforms through both direct and reflective links as
		\begin{equation}	\label{eq:y_k(t)}
			\begin{split}
				y_k(t)
				&=y_{I,k}(t)+y_{P,k}(t)	\\
				&=\Re\left\{{\sum_{n=1}^N{(w_{I,n}\tilde{x}_{I,n}(t)+w_{P,n})h_{k,n}e^{j2{\pi}{f_n}t}}}\right\}
				% &=\Re\left\{\sum_{n=1}^N{\boldsymbol{h}_{k,n}(\boldsymbol{w}_{P,n}+\boldsymbol{w}_{I,n}\tilde{x}_n)e^{j2{\pi}{f_n}t}}\right\}
			\end{split}
		\end{equation}

		% \begin{equation}	\label{eq:y_k**2(t)}
		% 	\begin{split}
		% 		\mathcal{A}\left\{y_{P,k}^2(t)=\frac{1}{2}\right\}
		% 		&=\Re\left\{\sum_{n_1,n_2}\right\}
		% 	\end{split}
		% \end{equation}
	\end{subsection}

	\begin{subsection}	{Information Decoder}
		One major benefit of using proposed waveform is that the deterministic power term $y_{P,k}(t)$ bears no information and creates no interference to the modulated information term $y_{I,k}(t)$. Therefore, the achievable rate of user $k$ is expressed as
		\begin{equation}	\label{eq:I_k}
			\begin{split}
				I_k(\boldsymbol{w}_I,\boldsymbol{\Theta},\rho)
				% &=\sum_{n=1}^N{\log_2\left(1+\frac{(1-\rho)\lvert\boldsymbol{h}_{k,n}\boldsymbol{w}_{I,n}\rvert^2}{\sigma_n^2}\right)}	\\
				&=\sum_{n=1}^N{\log_2\left(1+\frac{(1-\rho)(h_{k,n}w_{I,n})(h_{k,n}w_{I,n})^*}{\sigma_n^2}\right)}
			\end{split}
		\end{equation}
		where $\sigma_n^2$ is the sum variance of the Gaussian noise at the RF-band and those introduced during the RF-to-BB conversion on subband $n$. A significant conclusion in \cite{Clerckx2018b} indicates that the rate \ref{eq:I_k} is always achievable with or without waveform cancellation, by subtracting the deterministic power component or constructing a translated codebook.
	\end{subsection}

	\begin{subsection}	{Energy Harvester}
		Note that the information and power component $y_{I,k}(t)$ and $y_{P,k}(t)$ contribute to power transfer in different manners. Consider a nonlinear diode model based on the Taylor expansion of a small signal model \cite{Clerckx2018b,Clerckx2016a}, which highlights the dependency between the harvester output DC current and the received waveform by
		\begin{equation}	\label{eq:i_k}
			i_{\text{out},k}\approx\sum_{i=0}^{\infty}{k_i'}{\rho^{i/2}}{R_{\text{ant}}^{i/2}}\mathcal{E}_{\tilde{x}_n}\left\{{\mathcal{A}\left\{y_k(t)^i\right\}}\right\}
		\end{equation}
		where $k_i'$ depends on $i_{\text{out},k}$ and diode characteristics, $R_{\text{ant}}$ is the impedance of receive antenna. Once the composite channel response $h_{k,n}$ is fixed, the corresponding information and power weight $\boldsymbol{w}_I$, $\boldsymbol{w}_P$ are determined such that the randomness comes from the input distribution $\tilde{x}_n$. Therefore, we first extract the DC component based on $h_{k,n}$, $\boldsymbol{w}_I$, $\boldsymbol{w}_P$ by $\mathcal{A}\left\{.\right\}$ and then consider the expectation over $\tilde{x}_n$ by $\mathcal{E}\left\{.\right\}$. With the assumption of evenly spaced frequencies, $\mathcal{E}\left\{y^i(t)\right\}=0$ for odd $i$ which has no contribution to DC components. \cite{Clerckx2016a} also demonstrated that to maximize $i_{\text{out},k}$, it suffices to maximize the monotonic target function truncated to the $n_0$ order
		\begin{equation}	\label{eq:z_k}
			z_k(\boldsymbol{w}_I,\boldsymbol{w}_P,\boldsymbol{\Theta},\rho)=\sum_{i\,\text{even},i\ge2}^{n_0}{k_i}{R_{\text{ant}}^{i/2}}{\mathcal{E}\left\{y_k(t)^i\right\}}
		\end{equation}
		where $k_i=i_s/i!(nv_t)^i$, $i_s$ is saturation current, $n$ is diode ideality factor, $v_t$ is thermal voltage. We take $n_0=4$ to investigate the fundamental impact of diode nonlinearity on energy delivery. Since $\mathcal{E}\left\{\mathcal{A}\left\{y_{I,k}(t)y_{P,k}(t)\right\}\right\}=\mathcal{E}\left\{\mathcal{A}\left\{y_{I,k}^3(t)y_{P,k}(t)\right\}\right\}=\mathcal{E}\left\{\mathcal{A}\left\{y_{I,k}(t)y_{P,k}^3(t)\right\}\right\}=0$ and $\mathcal{E}\left\{\mathcal{A}\left\{y_{I,k}^2(t)y_{P,k}^2(t)\right\}\right\}=\mathcal{A}\left\{\mathcal{E}\left\{y_{I,k}^2(t)\right\}\right\}\mathcal{A}\left\{y_{P,k}^2(t)\right\}$, the target function $z_k$ reduces to \ref{eq:z_k_truncated}, whose terms are further expressed in \ref{eq:E{A{y_{I,k}**2}}} -- \ref{eq:A{y_{P,k}**4'}}.
		\begin{figure*}[b]
			\hrule
			\begin{equation}	\label{eq:z_k_truncated}
				\begin{split}
					z_k(\boldsymbol{w}_I,\boldsymbol{w}_P,\boldsymbol{\Theta},\rho)
					&={k_2}{\rho}{R_{\text{ant}}}\mathcal{E}\left\{\mathcal{A}\left\{y_{I,k}^2(t)\right\}\right\}+{k_4}{\rho^2}{R_{\text{ant}}^2}\mathcal{E}\left\{\mathcal{A}\left\{y_{I,k}^4(t)\right\}\right\}	\\
					&\quad+{k_2}{\rho}{R_{\text{ant}}}\mathcal{A}\left\{y_{P,k}^2(t)\right\}+{k_4}{\rho^2}{R_{\text{ant}}^2}\mathcal{A}\left\{y_{P,k}^4(t)\right\}	\\
					&\quad+6{k_4}{\rho^2}{R_{\text{ant}}^2}\mathcal{E}\left\{\mathcal{A}\left\{y_{I,k}^2(t)\right\}\right\}\mathcal{A}\left\{y_{P,k}^2(t)\right\}
				\end{split}
			\end{equation}
		\end{figure*}
		\begin{figure*}[b]
			\hrule

			\begin{align}
				\mathcal{E}\left\{\mathcal{A}\left\{y_{I,k}^2(t)\right\}\right\}
				 & =\frac{1}{2}\sum_n{(w_{I,n}h_{k,n})(w_{I,n}h_{k,n})^*}\label{eq:E{A{y_{I,k}**2}}}                                                                                                                                                                                                                                               \\
				 & =\frac{1}{2}\sum_n{\left[w_{I,n}(h_{D,k,n}+\boldsymbol{h}_{R,k,n}\boldsymbol{\Theta}_0\boldsymbol{h}_{I,n})\right]\left[w_{I,n}(h_{D,n,k}+\boldsymbol{h}_{R,k,n}\boldsymbol{\Theta}_0\boldsymbol{h}_{I,n})\right]^*}                                                                                                            \\
				\mathcal{E}\left\{\mathcal{A}\left\{y_{I,k}^4(t)\right\}\right\}
				 & =\frac{3}{4}\sum_{{n_1},{n_2}}{(w_{I,{n_1}}h_{k,{n_1}})(w_{I,{n_2}}h_{k,{n_2}})(w_{I,{n_1}}h_{k,{n_1}})^*(w_{I,{n_2}}h_{k,{n_2}})^*}                                                                                                                                                                                            \\
				 & =\frac{3}{4}\sum_{{n_1},{n_2}}\left[w_{I,{n_1}}(h_{D,k,n_1}+\boldsymbol{h}_{R,k,n_1}\boldsymbol{\Theta}_0\boldsymbol{h}_{I,n_1})\right]\left[w_{I,{n_2}}(h_{D,k,n_2}+\boldsymbol{h}_{R,k,n_2}\boldsymbol{\Theta}_0\boldsymbol{h}_{I,n_2})\right]\nonumber                                                                       \\
				 & \quad\left[w_{I,{n_1}}(h_{D,k,n_1}+\boldsymbol{h}_{R,k,n_1}\boldsymbol{\Theta}_0\boldsymbol{h}_{I,n_1})\right]^*\left[w_{I,{n_2}}(h_{D,k,n_2}+\boldsymbol{h}_{R,k,n_2}\boldsymbol{\Theta}_0\boldsymbol{h}_{I,n_2})\right]^*                                                                                                     \\
				\mathcal{A}\left\{y_{P,k}^2(t)\right\}
				 & =\frac{1}{2}\sum_n{(w_{P,n}h_{k,n})(w_{P,n}h_{k,n})^*}                                                                                                                                                                                                                                                                          \\
				 & =\frac{1}{2}\sum_n{\left[w_{P,n}(h_{D,k,n}+\boldsymbol{h}_{R,k,n}\boldsymbol{\Theta}_0\boldsymbol{h}_{I,n})\right]\left[w_{P,n}(h_{D,k,n}+\boldsymbol{h}_{R,k,n}\boldsymbol{\Theta}_0\boldsymbol{h}_{I,n})\right]^*}                                                                                                            \\
				\mathcal{A}\left\{y_{P,k}^4(t)\right\}
				 & =\frac{3}{8}\sum_{\substack{{n_1},{n_2},{n_3},{n_4}\\{n_1}+{n_2}={n_3}+{n_4}}}{(w_{P,{n_1}}h_{k,{n_1}})(w_{P,{n_2}}h_{k,{n_2}})(w_{P,{n_3}}h_{k,{n_3}})^*(w_{P,{n_4}}h_{k,{n_4}})^*}                                                                                                                      \\
				 & =\frac{3}{8}\sum_{\substack{{n_1},{n_2},{n_3},{n_4}\\{n_1}+{n_2}={n_3}+{n_4}}}\left[w_{P,{n_1}}(h_{D,k,n_1}+\boldsymbol{h}_{R,k,n_1}\boldsymbol{\Theta}_0\boldsymbol{h}_{I,n_1})\right]\left[w_{P,{n_2}}(h_{D,k,n_2}+\boldsymbol{h}_{R,k,n_2}\boldsymbol{\Theta}_0\boldsymbol{h}_{I,n_2})\right]\nonumber \\
				 & \quad\left[w_{P,{n_3}}(h_{D,k,n_3}+\boldsymbol{h}_{R,k,n_3}\boldsymbol{\Theta}_0\boldsymbol{h}_{I,n_3})\right]^*\left[w_{P,{n_4}}(h_{D,k,n_4}+\boldsymbol{h}_{R,k,n_4}\boldsymbol{\Theta}_0\boldsymbol{h}_{I,n_4})\right]^*\label{eq:A{y_{P,k}**4'}}
			\end{align}
		\end{figure*}
		Note that $\mathcal{E}\left\{\lvert\tilde{x}_n\rvert^2\right\}=1$ and $\mathcal{E}\left\{\lvert\tilde{x}_n\rvert^4\right\}=2$. The latter provides a modulation gain to the nonlinear terms in the output DC current.
